\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

% Page layout
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\setlength{\parindent}{0pt}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\fancyhead[L]{\textbf{Andrés Gordo Ortiz — Curriculum Vitae}}

% Hyperlink style
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
}

\begin{document}

% Header section
\noindent\textbf{Andrés Gordo Ortiz} \hfill \textit{Last Updated: \today} \\
BSc in Biotechnology \hfill \href{mailto:agordo@bistgraduatecentre.com}{agordo@bistgraduatecentre.com} \\
Born: 05/07/2002 \hfill \href{https://www.linkedin.com/in/andgortiz}{LinkedIn Profile} \\
\vspace{5pt}

% Experience
\section*{Experience}

\noindent\textbf{Centre for Genomic Regulation, Barcelona, Spain — MRes Student} \hfill Sept 2024 – Jul 2025 \\
\textit{MRes Thesis on Alternative Splicing and transcriptomics regulation by nuclear condensates in oocyte development, myoblast differentiation, and cancer using APEX2-Sequencing.} \\
Supervisor: Dr. Adel Al Jord, Co-Supervisor: Dr. Manuel Irimia \\
\textbf{Skills:} snRNA-seq, APEX2 pull-down, spatial transcriptomics, FACS sorting.

\vspace{10pt}

\noindent\textbf{LowSeq Bioinformatics, Spain — Founder} \hfill Apr 2024 – Present \\
\textit{Launched a bioinformatics service focusing on RNA-Seq, CHIP-Seq, Variant Calling using AWS EC2 and Nextflow. Developed custom R-Markdown reports and Shiny Apps.} \\
\href{https://lowseqbioinformatics.com}{LowSeq Website}

\vspace{10pt}

\noindent\textbf{Biotechnology Association of Aragón, Spain — Board Member} \hfill Sept 2023 – Sept 2024 \\
\textit{Led the Scientific Outreach branch, organized Biotechnofarm events for high school students, and represented ASBAR at FEBiotec.} \\
\href{https://asbaragon.es/}{ASBAR Website}

\vspace{10pt}

\noindent\textbf{Miguel Servet Hospital (IISAragón), Zaragoza, Spain — BSc Student} \hfill Sept 2023 – Jul 2024 \\
\textit{BSc thesis on cancer metabolism: Assessing the Phenotype of Pancreatic Cancer Stem Cells under Serine and Glycine deficiency.} \\
Supervisor: Dr. Patricia Sancho Andrés \\
\textbf{Skills:} Patient-derived xenografts, RNAseq, qPCR, Flow Cytometry.

\vspace{10pt}

\noindent\textbf{University College London, London, UK — Visiting Student} \hfill Jun 2023 – Sept 2023 \\
\textit{Internship studying novel light-based therapies in Pancreatic cancer.} \\
\textbf{Skills:} Cell Viability Assays, Immunofluorescence Microscopy, Western Blots.

\vspace{10pt}

% Education
\section*{Education}

\noindent\textbf{BIST Graduate Centre at Pompeu Fabra University, Barcelona, Spain — MMRES} \hfill Sept 2024 – Jul 2025 \\
\textit{Master of Multidisciplinary Research in Experimental Science.} \\
Master Thesis at CRG on transcriptomics and nuclear condensates.

\vspace{10pt}

\noindent\textbf{University of Zaragoza, Zaragoza, Spain — BSc in Biotechnology} \hfill Sept 2020 – Jul 2024 \\
\textit{Final Grade: 8.24/10. Class Speaker, Board Member, and Student Mentor.}

\vspace{10pt}

% Publications
\section*{Publications}

\begin{itemize}[leftmargin=1.5em]
    \item Espiau-Romera P, Gordo-Ortiz A, Ortiz-de-Solórzano I, Sancho P. \textit{Metabolic features of tumour-derived extracellular vesicles: challenges and opportunities.} Extracell Vesicles Circ Nucleic Acids 2024; 5:555-70.
    \item Gordo-Ortiz A. \textit{Targeting Cancer Stem Cells through Photodynamic Therapy.} Abstract \& talk at the 2nd SRUK/CERU Cancer Research Networking, 2023.
    \item Gordo-Ortiz A, Ortiz-de-Solórzano I, Navarro F. \textit{Cytokine-based immunotherapy in pancreatic cancer.} Book Chapter, International Review of Cell and Molecular Biology (submitted).
\end{itemize}

\vspace{10pt}

% Skills
\section*{Skills}

\noindent\textbf{Laboratory:} snRNA-seq, APEX2 pull-down, spatial transcriptomics, FACS sorting, RNAseq, qPCR, Flow Cytometry, Immunostaining, Metabolite Quantification. \\
\textbf{Bioinformatics:} RNA-Seq, CHIP-Seq, AWS EC2, Nextflow, Python, R, Bash.

\vspace{10pt}

% Languages
\section*{Languages}

\noindent\textbf{English:} Advanced (CAE) \\
\textbf{Spanish:} Native

\end{document}
